Review: The Prevalence of Adaptive Introgression in Crop Histories

### 2018-06-25 paper.tex
minor edits to titles

\title{Review: Adaptive Introgression Expanded the Genetic Base of Crops during Their post-Domestication Spread}

@@

In this review, we will: 1) briefly describe recently developed methods for detecting introgression, 2) present case studies suggesting wild-to-crop introgression has conferred local adaptation, 3) consider how introgression bears upon fundamental questions of domestication, and 4) describe future advances in both basic and applied genetics that can be made through the study of introgression in agroecosystems.

>>>>

\title{Review: The Prevalence of Adaptive Introgression in Crop Histories}

@@

In this review, we will: 1) briefly describe recently developed methods for detecting introgression, 2) present case studies suggesting wild-to-crop introgression has conferred local adaptation, 3) consider how introgression bears upon fundamental questions of domestication, and 4) describe remaining questions regarding crop adaptation through gene flow with wild relatives.
